Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-11-11 ms/main.tex
revise abstract

% Abstract
\begin{abstract}
We study the cultural evolution of cooperation under vertical and non-vertical cultural transmission.
Conditions are found for fixation and polymorphism of cooperation and defection. 
The evolution of cooperation is facilitated by horizontal transmission and by an association between social interactions and horizontal transmission.
The effect of oblique transmission depends on the horizontal transmission bias.
Stable polymorphism of cooperation and defection can occur.
When it does, selection favors the evolution of higher association between social interactions and horizontal transmission, which leads to an increased frequency of cooperation and higher population mean fitness.
The derived conditions are compared to outcomes of stochastic simulations of structured populations.
Comparisons are drawn with Hamilton's rule and the concepts of relatedness and assortment.
\end{abstract}

>>>>

% Abstract
\begin{abstract}
We study the cultural evolution of cooperation under vertical and non-vertical cultural transmission.
Conditions are found for fixation and coexistence of cooperation and defection. 
The evolution of cooperation is facilitated by horizontal transmission and by an association between social interactions and horizontal transmission.
The effect of oblique transmission depends on the horizontal transmission bias.
Stable polymorphism of cooperation and defection can occur.
When it does, selection will reduce the association between social interactions and horizontal transmission, which leads to a decreased frequency of cooperation and lower population mean fitness.
The derived conditions are compared to outcomes of stochastic simulations of structured populations.
Comparisons are drawn with Hamilton's rule and the concepts of relatedness and assortment.
\end{abstract}
